Hypertension and microbiome

### 2019-06-05 articletwo.Rmd
For night
Commenting

    res.trim <- map_df(res, ~map_df(.x, ~tidy(.x), .id = "taxa"), .id = "model")

    adonis <- res.trim %>%
        filter(term %in% var.BP) %>%
        group_by(model) %>%
        dplyr::mutate(q.value = p.adjust(p.value, method="BH")) %>%
        ungroup %>%
        arrange(q.value)

    res$MAP %>% names

adonis %>% pull(taxa) %>% sort

    adonis %>% dplyr::filter(taxa == "g_Sutterella")

map_df(res.trim$HYPERTENSION, ~

    maaslin <- map_df(res.trim, ~do.call(rbind, .x)) %>%
        dplyr::mutate(Qval = p.adjust(p.value, method="BH")) %>%
        arrange(Qval)

>>>>

    saveRDS(res, file = "rds/res.rds")

##     res.trim <- map_df(res, ~map_df(.x, ~tidy(.x), .id = "taxa"), .id = "model")

##     adonis <- res.trim %>%
##         filter(term %in% var.BP) %>%
##         group_by(model) %>%
##         dplyr::mutate(q.value = p.adjust(p.value, method="BH")) %>%
##         ungroup %>%
##         arrange(q.value)

##     res$MAP %>% names

## adonis %>% pull(taxa) %>% sort

##     adonis %>% dplyr::filter(taxa == "g_Sutterella")

## map_df(res.trim$HYPERTENSION, ~

##     maaslin <- map_df(res.trim, ~do.call(rbind, .x)) %>%
##         dplyr::mutate(Qval = p.adjust(p.value, method="BH")) %>%
##         arrange(Qval)

##     saveRDS(maaslin, file = "rds/maaslin.rds")
} else {
    maaslin <- readRDS("rds/maaslin.rds")
}
```
